Exploring Anomalies in Pacific Northwest Special Education Trends

### 2020-12-07 scripts/Final_project.Rmd
My turn to try to break everything
Correlogram code edits

BCdatastripped <- BCdata %>%

    select("SCHOOL_YEAR", 
         "DATA_LEVEL", 
         "SPECIAL_NEEDS_CODE", 
         "NUMBER_OF_STUDENTS", 
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER") %>% 
  filter(SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N") %>% 
    mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "High Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
           SCHOOL_YEAR = as.factor(SCHOOL_YEAR), 
           NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
           SCHOOL_YEAR = as.numeric(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 9)

@@

```{comprehensive display}

g_vic <- district_class %>%
  filter(DISTRICT_NAME == "Greater Victoria") %>%
  mutate(SCHOOL_YEAR = as.factor(SCHOOL_YEAR),
         SCHOOL_YEAR = as.numeric(SCHOOL_YEAR),
         SPECIAL_NEEDS_CODE = as.factor(SPECIAL_NEEDS_CODE),
          SPECIAL_NEEDS_CODE = as.numeric(SPECIAL_NEEDS_CODE),
         NUMBER_OF_STUDENTS = as.factor(NUMBER_OF_STUDENTS),
         NUMBER_OF_STUDENTS = as.numeric(NUMBER_OF_STUDENTS)) %>%
  select("SCHOOL_YEAR",
         "SPECIAL_NEEDS_CODE",
         "NUMBER_OF_STUDENTS") %>%
  as_tibble()

>>>>

BCdatastripped <- BCdata %>% 
    select("SCHOOL_YEAR", 
         "DATA_LEVEL", 
         "SPECIAL_NEEDS_CODE", 
         "NUMBER_OF_STUDENTS", 
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER") %>% 
  filter(SPECIAL_NEEDS_CODE != "M",
         SPECIAL_NEEDS_CODE != "J",
         SPECIAL_NEEDS_CODE != "N") %>% 
    mutate(SPECIAL_NEEDS_CODE = fct_recode(SPECIAL_NEEDS_CODE,
                          "Physically Dependent" = "A",
                          "Deafblind" = "B",
                          "Moderate+ ID" = "C",
                          "Chronic Health" = "D",
                          "Visual Impairment" = "E",
                          "Deaf or Hard of Hearing" = "F",
                          "Autism" = "G",
                          "High Behavioural Need" = "H",
                          "Mild ID" = "K",
                          "Learning Disability" = "Q",
                          "Gifted" = "P",
                          "Mild Behavioural Need" = "R"),
           SCHOOL_YEAR = as.factor(SCHOOL_YEAR), 
           NUMBER_OF_STUDENTS = as.integer(NUMBER_OF_STUDENTS),
           SCHOOL_YEAR = as.numeric(SCHOOL_YEAR)) %>% 
  filter(SCHOOL_YEAR >= 9)

@@

```{correllogram}

#cleaning data
bc_data_district_classification <- read_excel(here("data", "bc_data_district_classification.xlsx"))

x <- c(6,8)
district_class[ , x] <- apply(district_class[ , x], 2,
                               function(x)as.numeric(as.character(x)))
#creating data for cor
g_vic <- district_class %>%
  filter(DISTRICT_NAME == "Greater Victoria") %>%
  mutate(SCHOOL_YEAR = as.factor(SCHOOL_YEAR),
         SCHOOL_YEAR = as.numeric(SCHOOL_YEAR),
         SPECIAL_NEEDS_CODE = as.factor(SPECIAL_NEEDS_CODE),
          SPECIAL_NEEDS_CODE = as.numeric(SPECIAL_NEEDS_CODE),
         NUMBER_OF_STUDENTS = as.factor(NUMBER_OF_STUDENTS),
         NUMBER_OF_STUDENTS = as.numeric(NUMBER_OF_STUDENTS)) %>%
  select("SCHOOL_YEAR",
         "SPECIAL_NEEDS_CODE",
         "NUMBER_OF_STUDENTS") %>%
  as_tibble()
